TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-06 CORL/example.tex
Added images/main_diagram_condensed_with_domains.pdf
Added neural texture section

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}

@@

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
	\end{center}
	\caption{
		We use differentiable rendering paired with unpaired image translation to consistently transform synthetic scenes into realistic images.
		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses between nodes.
		Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
		$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/learnable_textures.pdf}
	\end{center}
	\caption{
		This figure illustrates how the differentiable, learnable textures are calculated in figure \ref{fig:main_diagram}.
		For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
	}
	\label{fig:learnable_textures}
\end{figure}

>>>>

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}

@@

The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values. The first two channels, U and V, are floating point values between 0 and 1. The L channel is also a floating point value between 0 and 1, it has a second meaning. There are only a finite number of label values (corresponding to the number of learnable textures). The rank of a particular L value is used to index these textures.

In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$. A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.

@@

\subsection{Neural Texture}

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
		\end{center}
		\caption{
			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:learnable_textures}
	\end{figure}

	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

	These neural textures are not stored in raster form during training. Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by a pixel-wise fourier feature network \cite{fourier_feature_networks} that takes in UV coordinates and returns RGB colors. During inference, however, these textures are rasterized to save both time and video memory.

	Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
	\makebox[\textwidth]
	{
		$
		\tau_i(uv) = 
		\
		M_i\left(\left[
			\sin f_1 uv, \ 
			\cos f_1 uv, \ 
			\sin f_2 uv, \ 
			\cos f_2 uv, \ 
			\dots \ 
			\sin f_{256} uv, \ 
			\cos f_{256} uv \ 
		\right]\right)
		$
	}
	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
	 $f_i uv$ represents their dot product, 
	%  $rgb$ represents a 3d color vector,
	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
	 $M_i: \mathbb{R}^{256} \rightarrow \mathbb{R}^3$.
	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.

	A particular neural texture $\tau_i$ uses maps $uv \rightarrow rgb$. Similarly, the set of textures $\tau_{1\dots L}$ maps uvl values to rgb values: $\tau_{1\dots L}(uvl)=\tau_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.

	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures. The trained fourier-feature textures also exhibit less noise than its raster counterparts. We think this is because they don't suffer as much from aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.

	% UV Map projection
	% We use an RGB texture, parametrized by an MLP taking fourier features as an input.
	% We use a separate MLP for every texture.

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
	\end{center}
	\caption{
		We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses between nodes.
		Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
		$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@
